Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-09-08 Response to reviewers.tex

\begin{verbatim}
Reviewer is right, so we have improved Section 5, including the 
parameter settings of M5P, kNN and RF methods (see paragraph XX at 
page YY), along with the configuration parameters for the rest of 
methods.

The authors want to express our gratitude to this reviewer 
for his/her suggestions.
\end{verbatim}
% Antonio - CONCERN: don't we also put the configuration of the rest of the methods? And say it. :D 
% Could we use a table for showing them easily?
% [pedro] TODO: design the table taken the parameters/values shown in section 5.1
% Antonio - TODO: say paragraph/page where they are.

% Antonio - TODO: Say if there are new references and include them in a final section in this letter.
% yes, there are some, but is Hossam who knows what references have been added in this revision.
%------------------------------------------------------------------------------------
\section{New references added after revision}

[53] G.B. Huang, Q.Y. Zhu, C.K. Siew, Extreme learning machine: theory and applications, Neurocomputing 70 (1) (2006) 489-501.
[54] G. Huang, G.B. Huang, S. Song, K. You, Trends in extreme learning machines: a review, Neural Networks 61 (2015) 32-48.
[71] M. A. Hall, Correlation-based feature selection for discrete and numeric class machine learning, in: Proceedings of the Seventeenth International Conference on Machine Learning, ICML2000, Morgan Kaufmann Publishers Inc., San Francisco, CA, USA, 2000, pp. 359-366.

### 2016-09-08 paper.tex
changing font for variable names

Initially, there were three different features describing the subjects
and subsubjects of every book \textit{subject1,2,3} (see Table
\ref{tabla:paramsOrig50}), but for most of the patterns (books) there
is no value for \textit{subjects2} and \textit{3}, so we have discarded 
these features.

With regard to the feature \textit{publisher}, it has been removed from the 
final dataset since it is indeed included in the code of \texttt{collection}. 
In addition, we think it is not really relevant for the accuracy of the models 
and, moreover, publishers probably will not want to use the results of other 
publishing companies for predicting their own sales.

@@

In the first stage of the experiments, forecasting methods have been
applied to the whole dataset. All the pre-sales features have been
considered, including the categorical ones, which makes it harder to
process the input patterns and build the different models. SVM for
instance, must previously transform these categories into binary
variables in order to deal with the data, which means the creation of
a different (and new) variable per each possible value. Thus, in the
case of \emph{publisher} or \emph{collection} this would imply the definition of
hundreds of new variables.

@@

Taking into account the obtained results by SVM model, this method obtains comparable 
errors to those of M5P. Even when using roughly tuned parameter values, it shows 
a good generalisation performance. However, SVM is much slower than the others to build 
the model, not only when using the dataset with categorical input variables, such 
as \emph{collection} and \emph{binding}, but also when using the datasets with 
numerical variables, not to mention the extra time needed to optimize its hyperparameters.

@@

%Moreover, in these experiments it has been seen the difficulty for some classifiers like the SVM to process information related to categorical variables, such as \emph{collection} and \emph{binding}.

@@

The dataset has also been analysed using SOM, and a visual exploration of the obtained results has been performed in order to determine the best variables to consider.
An important preprocessing step has been carried out before conducting the SOM analysis. Thus, the two categorical features \emph{collection} and \emph{binding} have been removed from the analysis since SOM cannot deal with them without a previous transformation into numerical ones. However, since they have a large number of unique different values this would be finally impracticable and useless.

@@

Examining the component planes shown in Figure \ref{fig:componentplanes}, it can be noticed that some variables have very similar colour maps which means that they are highly correlated. In this case, we have two examples; the first is the \emph{distrib\_novelty} and \emph{print\_run}variables while the second is the \emph{tot\_points\_sale} and \emph{tot\_points\_sale\_1st\_year}. In order to make the dataset having less number of uncorrelated features with each other, one of the redundant features is removed from each pair of features. Therefore, the \emph{distrib\_novelty} and \emph{tot\_points\_sale\_1st\_year} were omitted from the dataset.

>>>>

Initially, there were three different features describing the subjects
and subsubjects of every book \texttt{subject1,2,3} (see Table
\ref{tabla:paramsOrig50}), but for most of the patterns (books) there
is no value for \texttt{subjects2} and \texttt{3}, so we have discarded 
these features.

With regard to the feature \texttt{publisher}, it has been removed from the 
final dataset since it is indeed included in the code of \texttt{collection}. 
In addition, we think it is not really relevant for the accuracy of the models 
and, moreover, publishers probably will not want to use the results of other 
publishing companies for predicting their own sales.

@@

In the first stage of the experiments, forecasting methods have been
applied to the whole dataset. All the pre-sales features have been
considered, including the categorical ones, which makes it harder to
process the input patterns and build the different models. SVM for
instance, must previously transform these categories into binary
variables in order to deal with the data, which means the creation of
a different (and new) variable per each possible value. Thus, in the
case of \texttt{publisher} or \texttt{collection} this would imply the definition of
hundreds of new variables.

@@

Taking into account the obtained results by SVM model, this method obtains comparable 
errors to those of M5P. Even when using roughly tuned parameter values, it shows 
a good generalisation performance. However, SVM is much slower than the others to build 
the model, not only when using the dataset with categorical input variables, such 
as \texttt{collection} and \texttt{binding}, but also when using the datasets with 
numerical variables, not to mention the extra time needed to optimize its hyperparameters.

@@

%Moreover, in these experiments it has been seen the difficulty for some classifiers like the SVM to process information related to categorical variables, such as \texttt{collection} and \texttt{binding}.

@@

The dataset has also been analysed using SOM, and a visual exploration of the obtained results has been performed in order to determine the best variables to consider.
An important preprocessing step has been carried out before conducting the SOM analysis. Thus, the two categorical features \texttt{collection} and \texttt{binding} have been removed from the analysis since SOM cannot deal with them without a previous transformation into numerical ones. However, since they have a large number of unique different values this would be finally impracticable and useless.

@@

Examining the component planes shown in Figure \ref{fig:componentplanes}, it can be noticed that some variables have very similar colour maps which means that they are highly correlated. In this case, we have two examples; the first is the \texttt{distrib\_novelty} and \texttt{print\_run}variables while the second is the \texttt{tot\_points\_sale} and \texttt{tot\_points\_sale\_1st\_year}. In order to make the dataset having less number of uncorrelated features with each other, one of the redundant features is removed from each pair of features. Therefore, the \texttt{distrib\_novelty} and \texttt{tot\_points\_sale\_1st\_year} were omitted from the dataset.
